Clean data

### 2020-09-01 analysis/01_experimental-design.Rmd
Confirming hold-out levels and recoding continuous variables

@@

>>>>

The experimental design was created as part of the conjoint study in Qualtrics. Here we check to make sure that there is a balance across attribute levels (i.e., levels show up a roughly equal number of times for each attribute).

@@

Now we prepare the experimental design for use in estimating the model by dropping the first level of each attribute, which are all discrete, as the reference level.

### 2020-09-01 analysis/02_clean-data.Rmd
Confirming hold-out levels and recoding continuous variables

@@

@@

@@

@@

>>>>

    # *Q2.2*: How often do you follow international news? 
    # - Always
    # - Sometimes
    # - Never
    Q2.2 = fct_relevel(
      factor(Q2.2, labels = c("Always", "Sometimes", "Never")), 
      c("Never", "Sometimes", "Always")

@@

    # *Q2.6*: How much did you donate to charity last year?
    # - \$1 to \$49
    # - \$50 to \$99
    # - \$100 to \$499
    # - \$500 to \$999
    # - \$1000 to \$4,999
    # - \$5000 to \$9,999
    # - \$10,000 or more
    Q2.6 = factor(
      Q2.6, 
      labels = c(
        "$1-$49", "$50-$99", "$100-$499", "$500-$999", 
        "$1000-$4,999", "$5000-$9,999", "$10,000+"),
      ordered = TRUE
    # *Q2.7*: On a scale of not at all important (1) to essential (7), how important is it for you to trust charities?
    # - 1 (Not at all important)
    # - 2
    # - 3
    # - 4
    # - 5
    # - 6
    # - 7 (Essential)
    Q2.7 = factor(
      Q2.7,
      labels = c(
        "Not at all important", "Very unimportant", "Somewhat unimportant", 
        "Neutral", "Somewhat important", "Very important", "Essential"
      ordered = TRUE
    # *Q2.8*: On a scale of no trust at all (1) to complete trust (7), how much do you trust charities?
    # - 1 (No trust at all)
    # - 2
    # - 3
    # - 4
    # - 5
    # - 6
    # - 7 (Complete trust)
    Q2.8 = factor(
      Q2.8,
      labels = c(
        "No trust at all", "Very little trust", "Little trust", 
        "Neutral", "Some trust", "A lot of trust", "Complete trust"
      ordered = TRUE
    # *Q2.9*: Have you volunteered in the past 12 months?
    # - Yes
    # - No
    Q2.9 = fct_relevel(
      factor(Q2.9, labels = c("Yes", "No")), 
      c("No", "Yes")

@@

    # *Q5.1*: Did you vote in the last election?
    # - Yes
    # - No
    Q5.1 = fct_relevel(
      factor(Q5.1, labels = c("Yes", "No")), 
      c("No", "Yes")
    # *Q5.2*: On a scale of extremely liberal (1) to extremely conservative (7), how would you describe your political views?
    # - 1 (Extremely liberal)
    # - 2
    # - 3
    # - 4
    # - 5
    # - 6
    # - 7 (Extremely conservative)
    Q5.2 = factor(
      Q5.2,
      labels = c(
        "Extremely liberal", "Somewhat liberal", "Slightly liberal", "Moderate",
        "Slightly conservative", "Somewhat conservative", "Extremely conservative"
      ordered = TRUE

@@

    # *Q5.6*: On a scale of no trust (1) to complete trust (7), how much do you trust political institutions and the state?
    # - 1 (No trust)
    # - 2
    # - 3
    # - 4
    # - 5
    # - 6
    # - 7 (Complete trust)
    Q5.6 = factor(
      Q5.6,
      labels = c(
        "No trust at all", "Very little trust", "Little trust", 
        "Neutral", "Some trust", "A lot of trust", "Complete trust"
      ordered = TRUE
    # *Q5.7*: Have you ever traveled to a developing country? 
    # - Yes
    # - No
    Q5.7 = fct_relevel(
      factor(Q5.7, labels = c("Yes", "No")), 
      c("No", "Yes")

@@

    # *Q5.11*: On a scale of strongly agree (1) to strongly disagree (7), rate your response to the following statement: People should be more charitable towards others in society.
    # - 1 (Strongly agree)
    # - 2
    # - 3
    # - 4
    # - 5
    # - 6
    # - 7 (Strongly disagree)
    Q5.11 = fct_relevel(
      factor(
        Q5.11,
        labels = c(
          "Strongly agree", "Agree", "Somewhat agree", 
          "Neutral", "Somewhat disagree", "Disagree", "Strongly disagree"
        c(
          "Strongly disagree", "Disagree", "Somewhat disagree",
          "Neutral", "Somewhat agree", "Agree", "Strongly agree"
    # *Q5.12*: What is your gender?
    # - Male
    # - Female
    # - Transgender
    # - Prefer not to say
    # - Other: _________
    Q5.12 = factor(
      Q5.12, 
      labels = c(
        "Male", "Female", "Transgender", 
        "Prefer not to say", "Other"
      ordered = TRUE
    # *Q5.13*: Are you now married, widowed, divorced, separated, or never married?
    # - Married
    # - Widowed
    # - Divorced
    # - Separated
    # - Never married
    Q5.13 = factor(
      Q5.13, 
      labels = c(
        "Married", "Widowed", "Divorced", 
        "Separated", "Never married"
      ordered = TRUE
    # *Q5.14*: What is the highest degree or level of school you have completed?
    # - Less than high school
    # - High school graduate
    # - Some college
    # - 2 year degree
    # - 4 year degree 
    # - Graduate or professional degree
    # - Doctorate
    Q5.14 = factor(
      Q5.14, 
      labels = c(
        "Less than high school", "High school graduate", 
        "Some college", "2 year degree", "4 year degree", 
        "Graduate or professional degree", "Doctorate"
      ordered = TRUE
